STA107 Post-Course Survey Analysis

### 2025-04-15 paper/paper.qmd
updated pdf
final version

```{r theme-table, echo=FALSE}
knitr::kable(theme_table, caption = "Themes Identified per Open-Ended Question")
```

@@

#### 3. Clarity and Structure of Assignments (Q16)
- **Sub-theme**: Assignment purpose unclear
- **Sub-theme**: Difficulty with concepts
- **Frequency**: ~26 mentions
> "Sometimes it was hard to understand the purpose of the task."

>>>>

```{r theme-table, echo=FALSE}
knitr::kable(question_theme_mapping, caption = "Themes Identified per Open-Ended Question")
```

@@

#### 3. Clarity and Structure of Assignments (Q16)
- **Sub-theme**: Perceived challenge in task content
- **Sub-theme**: Interpretation of assignment expectations
- **Reflection**: Several students noted that assignments were challenging. This likely reflects the complex and mathematical nature of the content, an intentional design element aimed at promoting deeper learning. 
> "The assignments are not easy and you need to think critically to figure them out."
